\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{tikz}
%\usepackage{hyperref}
%\usetikzlibrary{automata,positioning}
%\usepackage{graphicx}
%\graphicspath{ {images/} }
\usepackage[linewidth=1pt]{mdframed}
%\usepackage{algorithm}
%\usepackage{algpseudocode}
\usepackage{fancyhdr}
%\usetikzlibrary{decorations, decorations.text,}

\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

%\pagestyle{fancy}
%\lhead{Name: Anjana Tiha}
%\chead{}
%\rhead{Information Retrieval and Web Search(COMP 8130)}
%\lfoot{}
%\cfoot{Page \thepage}
%\rfoot{\today, Fall, 2017}

\begin{document}

	\begin{titlepage}
		
		\begin{center}
			\begin{large}
			\vspace*{11em}
			\textbf{
			Research Paper Summery\\
			\vspace{2em}
			Paper Title: A Survey on Text Summarization Techniques and Recent Trends \\
			\vspace{2em}
			Course Name: Information Retrieval/Web Search(COMP 8130)\\
			\vspace{0.5em}
			Course taken by: Prof. Vasile Rus\\
			\vspace{2em}
			Submitted by\\
			\vspace{1em}
			Student Name: Anjana Tiha\\
			UID: U00619942\\
			Date: 09/11/2017\\
			}
			\end{large}

		\end{center}
		
	\end{titlepage}
	\newpage
	
	
\section*{Summery: }
Text summarization is the process of generating shorter and condensed text from one or more larger textual sources. Text summarization is specially helpful when user have less shorter time or large number of documents to comprehend. Currently, there are many techniques used for generating summery. One of the technique involves scoring sentences based on sentence features and selecting sentences to generate summery on the document. Some common features for scoring sentences includes sentence length, sentence position, TF-IDF etc. Also, oftentimes words in each sentence are given weights based on term importance and then sentences are ranked by calculating the overall importance of the all the words present in that sentence. Recently, recurrent neural network has been used for generating summery. Recurrent neural network has advantage of preserving semantic relation and long short memory. Unsupervised technique like centroid based summarization are also used where sentences are scored based on similarities and relative positions. Context based summarization is another technique, where features for scoring sentences are chosen based on the context. The purpose of the paper is to survey on these popular summarization techniques and trends.



\end{document}

